### 2020-06-01 README.Rmd
small changes ahead of resubmission
recompiled site; added info about potential install failures to readme

``` r
devtools::install_github("richarddmorey/Morey_Hoekstra_StatCognition", build_vignettes = TRUE, depedencies = TRUE)
```

>>>>

``` r
devtools::install_github("richarddmorey/Morey_Hoekstra_StatCognition", build_vignettes = TRUE, dependencies = TRUE)
```

### Problems installing

If you have difficulties installing the package due to failure to compile the vignettes &mdash; particularly on Windows &mdash; you can try setting `build_vignettes` to `FALSE` in the command above. You can also move your R installation and temp folder to a location without spaces. This is a good idea even if turning off compilation of the vignettes solves the immediate problem. See [here](https://lcolladotor.github.io/2019/09/18/windows-user-space-issues-with-installing-r-packages/) for details.
